NOPT048 Notes

### 2020-04-23 misc/study-notes/math457.tex
K infinite
Some mistakes in Algebra 4

For a unital commutative ring $R$, we define the {\it nilradical} of $R$ to be the intersection $\Nil(R) = \bigcap P$ of all prime ideals $P$. The {\it Jacobean radical} is the intersection $\Jac(R) = \bigcap M$ of all maximal ideals $M$. Since $\Specmax(R) \subseteq \Spec(R)$, $\Jac(R) \supseteq \Nil(R)$. An element $r\neq 0$ in a ring $R$ is called {\it nilpotent} if $r^n = 0$ for some $n$. It turns out that there is a connection between nilpotency and prime ideals.

@@

\proof. Let $p\in R$ be a prime element. Assume that $p=ab$. This implies that $p\setminus a$ or $p\setminus b$. Say $a = pc$ for some $c\in R$. Then $p=ab=pcb$ and $cb = 1$. So $b$ is a unit.\slug

@@

\proof. Let $a,b\in \Z[i]$, $b\neq 0$. We can divide them in $\C$ to get $z = a/b$. Then there is a (not necessarily unique) $q\in \Z[i]$ that is of minimal distance to $z$. We have $|z-q|<1$; in fact $|z-q| \leq \sqrt{2}/2 < 1$. So $|a-bq| < |b|$.\slug

@@

Let $R$ be a a unital commutative ring. A {\it module} $M$ over $R$ is a ring homomorphism $R\to \End(M)$. Explicitly, the list of axioms of a module are very similar to those of a vector space (in fact, if $R$ is a field, then a module is a vector space). For $r,s\in R$ and $m,n\in M$, we have
\medskip
\item{i)} $r(m+n) = rm + rn$;
\smallskip
\item{ii)} $(r+s)m) = rm + sm$;
\smallskip
\item{iii)} $(rs)m = r(sm)$;
\smallskip
\item{iv)} $1m = m$.
\medskip
These axioms also work if $R$ is not commutative; in this case, we call $M$ a {\it left $R$-module}. The kernel of $R\to \End(M)$ is called the {\it annihilator} of $M$:
$$\Ann(M) = \{r\in R : rm = 0\ \hbox{for all}\ m\in M\}$$
A module is said to be {\it faithful} if $\Ann(M)$ is trivial. If $M$ is an $R$-module, then $M$ is a faithful $S$-module where $S = R/\Ann(M)$.

@@

\proof We can suppose that $L$ is infinite, since otherwise $K$ is finite and we can let $\gamma$ be a primitive root of unity that generates $K^\times$. Moreover, it suffices to show the theorem for two elements $\alpha$ and $\beta$, with $\beta$ separable, since a simple induction will extend the result to arbitrary $n$. Let $f$ and $g$ be irreducible polynomials for which $\alpha$ and $\beta$ are roots, respectively. Let $\alpha_1,\ldots,\alpha_r$ be the distinct roots of $f$ and $\beta_1,\ldots,\beta_s$ be roots of $g$; let $\alpha =\alpha_1$ and $\beta = \beta_1$.

>>>>

For a unital commutative ring $R$, we define the {\it nilradical} of $R$ to be the intersection $\Nil(R) = \bigcap P$ of all prime ideals $P$. The {\it Jacobson radical} is the intersection $\Jac(R) = \bigcap M$ of all maximal ideals $M$. Since $\Specmax(R) \subseteq \Spec(R)$, $\Jac(R) \supseteq \Nil(R)$. An element $r\neq 0$ in a ring $R$ is called {\it nilpotent} if $r^n = 0$ for some $n$. It turns out that there is a connection between nilpotency and prime ideals.

@@

\proof Let $p\in R$ be a prime element. Assume that $p=ab$. This implies that $p\setminus a$ or $p\setminus b$. Say $a = pc$ for some $c\in R$. Then $p=ab=pcb$ and $cb = 1$. So $b$ is a unit.\slug

@@

\proof Let $a,b\in \Z[i]$, $b\neq 0$. We can divide them in $\C$ to get $z = a/b$. Then there is a (not necessarily unique) $q\in \Z[i]$ that is of minimal distance to $z$. We have $|z-q|<1$; in fact $|z-q| \leq \sqrt{2}/2 < 1$. So $|a-bq| < |b|$.\slug

@@

Let $R$ be a a unital commutative ring. A {\it module} $M$ over $R$ is a ring homomorphism $R\to \End(M)$. Explicitly, the list of axioms of a module are very similar to those of a vector space (in fact, if $R$ is a field, then a module is a vector space). For $r,s\in R$ and $m,n\in M$, we have
\medskip
\item{i)} $r(m+n) = rm + rn$;
\smallskip
\item{ii)} $(r+s)m = rm + sm$;
\smallskip
\item{iii)} $(rs)m = r(sm)$;
\smallskip
\item{iv)} $1m = m$.
\medskip
These axioms also work if $R$ is not commutative; in this case, we call $M$ a {\it left $R$-module}. The kernel of $R\to \End(M)$ is called the {\it annihilator} of $M$:
$$\Ann(M) = \{r\in R : rm = 0\ \hbox{for all}\ m\in M\}$$
A module is said to be {\it faithful} if $\Ann(M)$ is trivial. If $M$ is an $R$-module, then $M$ is a faithful $S$-module where $S = R/\Ann(M)$.

@@

\proof We can suppose that $K$ is infinite, since otherwise we can let $\gamma$ be a primitive root of unity that generates $K^\times$. Moreover, it suffices to show the theorem for two elements $\alpha$ and $\beta$, with $\beta$ separable, since a simple induction will extend the result to arbitrary $n$. Let $f$ and $g$ be irreducible polynomials for which $\alpha$ and $\beta$ are roots, respectively. Let $\alpha_1,\ldots,\alpha_r$ be the distinct roots of $f$ and $\beta_1,\ldots,\beta_s$ be roots of $g$; let $\alpha =\alpha_1$ and $\beta = \beta_1$.
